---
title: "LAER(ANOVA)"
author: "edmar.teixeira@me.com"
date: "Thursday, February 26, 2015"
output: html_document
---

# Data from Fodder Beet Emmanuel's P21 trials 2012
# ANOVA of area expansion and senescence coefficient between irrigated an drain-fed plots

```{r}
library(agricolae)
```



Change dir
```{r, echo =FALSE, include=FALSE}
#Change the directory workspace
setwd("C:\\MyPfrBackUp\\My papers\\2015-Emmanuels_FodderBeet_Canopy\\Stats\\laer")
```

Read file
```{r, echo =FALSE, include=FALSE}
# Read files from stats folder load it to a variable
info  = read.table("laer(anova).txt", sep="\t", header=T)
info
```

sort factors
```{r, echo =FALSE, include=FALSE}
info$Rep <- as.factor(info$Rep)
info$NitroTreat <- as.factor(info$NitroTreat)
```

Summary

Here's the data
```{r}
summary (info)
info
```


# Experiment A (LAER)

Expansion rates in EXP A

```{r, echo =FALSE, include=TRUE}
expA = subset (info, Experiment == "A")
expA
anova = aov(LAER ~ WaterTreat+Rep, data = expA)
summary(anova)

# run a Tukey test if there are differences
TukeyHSD(anova)

boxplot(expA$LAER ~ expA$WaterTreat, names.arg=c("Rainfed","Irrigated"))
round(mean(expA$LAER[expA$WaterTreat=="RainFed"]), digits = 4)

hsd = HSD.test(anova, "WaterTreat", alpha = 0.05)
hsd
# HSD
hsd$statistics$HSD

```


### Water stress reduced LAER from **`r round(mean(expA$LAER[expA$WaterTreat=="Irrigated"]), digits = 4)    `** in irrigated to **`r round(mean(expA$LAER[expA$WaterTreat=="RainFed"]), digits = 4)    `** in rain-fed


## Experiment A (LASR)

Senescence rates in experiment A

```{r}
expA = subset (info, Experiment == "A")
expA
anova = aov(LASR ~ WaterTreat+Rep, data = expA)
summary(anova)

# run a Tukey test if there are differences
TukeyHSD(anova)

boxplot(expA$LASR ~ expA$WaterTreat, names.arg=c("Rainfed","Irrigated"))

hsd = HSD.test(anova, "WaterTreat", alpha = 0.05)
hsd
# HSD
hsd$statistics$HSD

```


### Water stress **increased** LASR (P<0.028) from **`r round(mean(expA$LASR[expA$WaterTreat=="Irrigated"]), digits = 4)    `** in irrigated to **`r round(mean(expA$LASR[expA$WaterTreat=="RainFed"]), digits = 4)    `** in rain-fed


# Experiment B (LAER)

Expansion rates using the late data of max LAI (April)

```{r, echo =FALSE, include=TRUE}
expB = subset (info, Experiment == "B")
expB
anova = aov(LAER ~ WaterTreat*NitroTreat+Rep, data = expB)
summary(anova)

# run a Tukey test if there are differences
TukeyHSD(anova)

boxplot(expB$LAER ~ expB$WaterTreat*expB$NitroTreat, names.arg=c("Rainfed\nNito","Irrigated","",""), las=2)

par(mfrow=c(1,2))
boxplot(expB$LAER ~ expB$WaterTreat, las=2)

boxplot(expB$LAER ~ expB$NitroTreat, las=2)

hsd <- HSD.test(anova, c("NitroTreat", "WaterTreat"), group=TRUE, alpha = 0.05)
hsd
# HSD
hsd$statistics$HSD

```

# Experiment B (LAER2)

Expansion rates using an early date of reaching LAI max (February) because the effect of water is only evident in the first part of the regrowth (when N effect is negligible) as there was rain in the end when N effect appeared


```{r, echo =FALSE, include=TRUE}
expB = subset (info, Experiment == "B")
expB
anova = aov(LAER2 ~ WaterTreat*NitroTreat+Rep, data = expB)
summary(anova)

# run a Tukey test if there are differences
TukeyHSD(anova)

boxplot(expB$LAER2 ~ expB$WaterTreat*expB$NitroTreat, names.arg=c("Rainfed\nNito","Irrigated","",""), las=2)

par(mfrow=c(1,2))
boxplot(expB$LAER2 ~ expB$WaterTreat, las=2)

boxplot(expB$LAER2 ~ expB$NitroTreat, las=2)


hsd <- HSD.test(anova, c("NitroTreat", "WaterTreat"), group=TRUE, alpha = 0.05)
hsd
# HSD
hsd$statistics$HSD

```


## Experiment B (LASR)
```{r, echo=FALSE, include=TRUE}
expB = subset (info, Experiment == "B")
expB
anova = aov(LASR ~ WaterTreat*NitroTreat+Rep, data = expB)
summary(anova)

# run a Tukey test if there are differences
TukeyHSD(anova)

boxplot(expB$LASR ~ expB$WaterTreat*expB$NitroTreat, names.arg=c("Rainfed\nNito","Irrigated","",""), las=2)

par(mfrow=c(1,2))
boxplot(expB$LASR ~ expB$WaterTreat, las=2)

boxplot(expB$LASR ~ expB$NitroTreat, las=2)


hsd <- HSD.test(anova, c("NitroTreat", "WaterTreat"), group=TRUE, alpha = 0.05)
hsd
# HSD
hsd$statistics$HSD
```



