---
title: "PhylloFodderBeetBrokenStick"
author: "edmar.teixeira@me.com"
date: "Friday, February 14, 2015"
output: html_document
---

## Method
Piece-wise functions with two or three segments were used to empirically describe the relationship between the number of senesced leaves and thermal-time accumulation. The inverse of the slope of each segment gave an estimate of the rate of senescence (oCd/senesced leaf) for a given range of Tt accumulation.

Analysis were performed with the software R using the "segmented" package.
```{r Libs, echo=FALSE, include=FALSE}
library(segmented)
library(ggplot2)
```

## Read files from stats folder load it to a data frame
```{r ReadFile, echo=FALSE, include=TRUE}
setwd ("C:\\MyPfrBackUp\\My papers\\2015-Emmanuels_FodderBeet_Canopy\\Stats\\senesc\\")
info  = read.table("Broken_Stick_Senesc_Tt.txt", sep="\t", header=T)
head(info)
#plot(info)
```

##Identify factors
```{r Treats, echo=FALSE, include=FALSE}
years = unique(info$Year)
waterTreats = unique(info$Water)
years
waterTreats
```

## Calculates the piece-wise functions

```{r echo=FALSE, include=TRUE}
par(mar=c(5,7,4,2))
par(mfcol=c(2,2))
graphNo=0
g = NULL
maxY <- max(info$Leaves)
for(y in 1:length(years)) {
  for(w in 1:length(waterTreats)) {
      
    graphNo = graphNo + 1
    
        if(graphNo == 1) {graphTitle = "A"
                }else{
                  graphTitle = "B"}
    
    df = subset(info, Year == years[y] & Water == waterTreats[w])
    
    if(w == 2 & y == 2) { # if rainfed break and exp B it twice
      
      out.lm<-lm(Leaves~Tt,data=df)
      o<-segmented(out.lm,seg.Z=~Tt,psi=list(Tt=c(1500,2000)),
                   control=seg.control(display=FALSE))
      # show stats
      print(summary(o))
      
      # find slopes and phyllochron
      s = slope(o)
      phyl = round(1/s$Tt[,1], digits = 0)
      
      # find breaks
      b = o$psi[,2]
      
      # show slopes and breakpoints
      print(paste0(years[y], "_",waterTreats[w],
                   ": Slopes: ", phyl, "oCd ", 
                   " Breaks at ",round(b, digits = 0), "oCd "))
      
      # plot graph
      plot(df$Tt,df$Leaves,cex=1.8, pch=01, family= "serif", xlab="", ylab="", ylim=c(0,maxY))
      plot(o,lwd=3, add=T)
      title(xlab=expression("Thermal-time ("^"o"~"Cd)"), 
      family= "serif", cex.lab=1.3, cex.main=1.3, cex.axis=1.3,  
      ylab = expression("Leaves per plant ("~ italic("n") ~")") )
      mtext(letters[graphNo], side = 3, line = -2, adj = 0.05, cex = 1, col = "grey40")
      
      # get the fitted data
      my.fitted <- fitted(o)
      my.model <- data.frame(Tt = df$Tt, Leaves = my.fitted)

      # plot the fitted model
     # g[graphNo] = ggplot(my.model, aes(x = Tt, y = Leaves)) + geom_line()
    
    } else {
      
      out.lm<-lm(Leaves~Tt,data=df)
      o<-segmented(out.lm,seg.Z=~Tt,psi=list(Tt=1800),
                   control=seg.control(display=FALSE))    
      # show stats
      print(summary(o))
      
      # find slopes and phyllochron
      s = slope(o)
      phyl = round(1/s$Tt[,1], digits = 0)
      
      # find breaks
      b = o$psi[,2]
      
      # show slopes and breakpoints
      print(paste0(years[y], "_",waterTreats[w],
                   ": Slopes: ", phyl, "oCd ", 
                   " Breaks at ",round(b, digits = 0), "oCd "))
      if (w == 1) {
        theTitle <- as.character(paste0("Experiment ",graphTitle))
      } else {
        theTitle <- NULL
      }
      
      
      # plot graph
      plot(df$Tt,df$Leaves, family= "serif", cex=1.8, cex.main=1.5, pch=01, 
           main= theTitle, xlab="", ylab="", ylim=c(0,maxY)) 
      plot(o,lwd=3, add=T)
      title(xlab=expression("Thermal-time ("^"o"~"Cd)"), family= "serif", 
            cex.lab=1.3, cex.main=1.3, cex.axis=1.3, 
            ylab = expression("Leaves per plant ("~ italic("n") ~")") )
      mtext(letters[graphNo], side = 3, line = -2, adj = 0.05, cex = 1, col = "grey40")
      
 
      # get the fitted data
      my.fitted <- fitted(o)
      my.model <- data.frame(Tt = df$Tt, Leaves = my.fitted)

      # plot the fitted model
      #ggplot(my.model, aes(x = Tt, y = Leaves)) + geom_line()
      
    }
  }
}
```

